**Density Dependence**

### 2023-02-09 Rmd/ddMac.Rmd
works!

for (year in dimnames(om2)$year[-1]){

  #stock.wt(   om2)[,year]=ddWt(stock.wt(om2)[,year],biomass(om2)[,ac(an(year))],par["bmsy"])
  #landings.wt(om2)[,year]=stock.wt(om2)[,year]*lsr[,year]
  #discards.wt(om2)[,year]=stock.wt(om2)[,year]*dsr[,year]

  #mat(om2)[,year]=1/(1+exp(-par["k"]*(stock.wt(om2)[,year]-par["w50"])))
  #m(  om2)[,year]=par["m1"]%*%(stock.wt(om2)[,year]%^%par["m2"])

  #om2=fwd(om2,f=f[,year],sr=eq)}

  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }
catch(om2)=computeCatch(om2,slot="all")
```

>>>>

for (year in dimnames(om2)$year[-1]){
  om2=ddFn(year,om2,par)
  om2=fwd(om2,f=f[,year],sr=eq)
  }
catch(om2)=computeCatch(om2,slot="all")
```
